Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
diff figure better introduced, kept in
added FIXME in intro
improved bar alignment explanation

One major issue in working with small patches concerns temporal
alignment.  [explain bar alignment]

@@

\subsection{Cluster}
Once we understand the kind of codebook we create, we naturally want
to visualize the clusters, \ie the patterns from actual song that
surround a given centroid. Unsurprisingly, real patterns tend to be
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering. In Figure \ref{fig:cluster} we show elements of the same
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid.

FIXME: we want the differences to be close to uniformly random, right
(hence centroid)?
And that's kind of what they look like.  Does Fig
\ref{fig:cluster_diff} really add much?

@@

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to FIXME ... 
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

@@

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats in the test set.  As
we mentioned before, $4$ beats is the most common bar size using the
Echo Nest segmentation. We then encode this sequence using an offset
of $0$, $1$, $2$ or $3$ beats. The best offset in terms of distortion
should correspond to the bar alignment in the original
feature matrix.  The correct answer is an offset of $0$.

FIXME: Actually I'm (ronw) not sure how this was done.  Every 4 beat
segment was treated separately?  Its not looking for a per-song alignment?

>>>>

One major issue in working with small patches concerns temporal
alignment.  FIXME: [explain bar alignment]

@@

\subsection{Cluster}
Once we understand the kind of codebook we create, we naturally want
to visualize the clusters, \ie the patterns from actual song that
surround a given centroid. Unsurprisingly, real patterns tend to be
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering. In Figure \ref{fig:cluster} we show elements of the same
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.

%FIXME: we want the differences to be close to uniformly random, right
%(hence centroid)?
%And that's kind of what they look like.  Does Fig
%\ref{fig:cluster_diff} really add much?

@@

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to supervised tasks. The representation created from large collections
captures meaningful information without being forced to do so.
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

@@

We train a codebook of size $100$ on bars resized to $4$ beats. Then,
we take the longest sequence of bars of $4$ beats for each song
in the test set.  As
we mentioned before, $4$ beats is the most common bar size using the
Echo Nest segmentation. We then encode each of these sequences using an offset
of $0$, $1$, $2$ or $3$ beats. The best offset for a test sequence
(the one with the lowest distortion)
should correspond to the bar alignment in the original
feature matrix.  The correct answer is an offset of $0$.

%FIXME: Actually I'm (ronw) not sure how this was done.  Every 4 beat
%segment was treated separately?  Its not looking for a per-song alignment?
%TBM: yes, I simply summed the divergence from all patterns for a given
% divergence, the lowest sum is the winner. So it's a per-song alignment.
